\documentclass{screenplay}[2012/06/30]
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\title{Mictlan}
\author{Jessica Flores}

\begin{document}

\coverpage
\fadein


\intslug [night]{empty space}


\begin{dialogue}{Nikniu}
In the begining, there was nothing, the world was empty that's why the first gods gave birth to the main gods of creation 
\end{dialogue}

Four lights appear in the darkness 


\intslug[afternoon]{Cipactli}

Quetzalcoatl and Tezcatlipoca fight together against Cipactli
\begin{dialogue}[continuing]{Nikniu}
Two of them, were Quetzalcoatl and Tezcatlipoca, together, they fought against the mostrous sea creature Cipactli, Tezcatlipoca needed to sacrifice his leg to assure their victory, with this, they were able to give form to the land and the sky, just as we know it
\end{dialogue}


\intslug[day]{landscape}

Volcanoes, heavy winds and floods destroy separeted the land
\begin{dialogue}[continuing]{Nikniu}
After that, different failed attemps for creating the perfect humankind were made. In order to get rid of the failures, the world suffered distinct catastrophes
\end{dialogue}

\intslug[night]{Inside a cave}
\begin{dialogue}[continuing]{Nikniu}
The remaining bones of the now extincted humans where abandoned and forgoten. And so, the time passed....
\end{dialogue}

\fadein
\intslug[day]{Teotihuacan}

Quetzalcoatl is waiting nervously at the center of a reunion place waiting for his brothers and other gods to arrive

\begin{dialogue}[walks and see the sky with preocupation]{Quetzalcoatl}

\end{dialogue}

A group of gods arrive, and as they take sit on any rock, one of them approaches to Quetzalcoatl

\begin{dialogue}{Xipetotec}
So, why did you call all of us in here, brother?
\end{dialogue}

\begin{dialogue}[continuing]{Quetzalcoatl}
The past humanities were a failure, but, I found a solution , if we combine the best of them and fix their mistakes, a perfect new humanity can be created! 
\end{dialogue}

All of the presents start murmuring and begin to refuse Quetzalcoatls plan

\begin{dialogue}{some random god}
You cannot combine what it's gone, and nothing of them remains in the world
\end{dialogue}

Quetzalcoatl felt discourage
Tezcatlipoca stood up and start talking

\begin{dialogue}[mocking tone]{Tezcatlipoca}
HEY! Do I need you all to remember that there are still remainings of all YOUR failures in the deepest part of Mictlan? 
\end{dialogue}

Mictlantecuhtli stood up aggressivily
\begin{dialogue}[angry]{Mictlantecuhtli}
The ancient were dangerous, unify them will cause more destruction than the last times. So for the sake of everything don't you dare to go near of those bones, if you do, you'll not be well received in my domains!
\end{dialogue}

Mictlantecuhtli dissappears in a smoke cloud


\begin{dialogue}[kind of nervous]{Xipetotec}
Brother, Mictlantecuhtli is dangerous, you shouldn't take his words lightly.
\end{dialogue}


\begin{dialogue}{Quetzalcoatl}
I have no option, I'll go and recover those bones
\end{dialogue}

Quetzalcoatl walks in the direcction of Tezcatlipoca, and this stops Quetzalcoatl
\begin{dialogue}[confident]{Tezcatlipoca}
I'll go with you
\end{dialogue}

\centretitle{THE LEGEND}

Quetzalcoatl and Tezcatlipoca start flying to Mictlan


\intslug{the sky}
\begin{dialogue}{Tezcatlipoca}
 The entrance must be near here!
\end{dialogue}

Out of nowhere a giant cloud appeared blinding Quetzalcoatl, as a fierce storm begins


\begin{dialogue}[stop flying and started seraching for his brother]{Quetzalcoatl}
 Tezcatlipoca! where are you! 
\end{dialogue}


\begin{dialogue}{Tezcatlipoca}
I'm over here! This storm may be work of Mictlantecuhtli! 
\end{dialogue}


\begin{dialogue}{Quetzalcoatl}
 Where? I can't see you! 
\end{dialogue}

A strong lighting sounds 

\intslug {a kind of jungle inside a cavern}

\begin{dialogue}[confused]{Quetzalcoatl}
Where am I?
\end{dialogue}

\centretitle{BEGINS}

\intslug {Snow mountains}
An iced giant bird shows in front of Quetzalcoatl


\begin{dialogue}{Nikniu}
You are in Mictlan
\end{dialogue}


\intslug {Obsidian place}
Quetzalcoatl attacks Itzlacoliuhqui
\begin{dialogue}{Quetzalcoatl}
Where's my brother?! 
\end{dialogue}

\centretitle{HERE}

\intslug [night]{in a desert}

Nexocho materialice 
\begin{dialogue}{Fear's god Nexocho}
You've make it well, but your end is here.
\end{dialogue}

\intslug {dark}
\begin{dialogue}[shouting]{Quetzalcoatl}
Nikniu!!!!
\end{dialogue}

\intslug [night]{In ancient ruins}
\begin{dialogue}{Mictlantecuhtli}
You have guts for coming this far Quetzalcoatl, let's see what you can do
\end{dialogue}

\centretitle{MICTLAN}

\intslug{In front a lake}
\begin{dialogue}{Quetzalcoatl}
So, why am I watching this boring bird Nikniu?
\end{dialogue}

\begin{dialogue}[smiling]{Nikniu}
Nothing in particular, I just thought you could like it, it's pretty right?
\end{dialogue}

Quetzalcoatl stare at Nikniu clearly mad

\end{document}
